Compare pseqs

### 2019-05-23 comparepseqs.Rmd
Minor
As numeric

    if ("subset" %in% names(args))
        subset.run <- args$subset
}
```

@@

```{r subset runs}
if (exists(subset.run)) {
    rds <- rds[[subset.run]]
}

print(rds)
quit()
```

>>>>

    if ("subset" %in% names(args))
        subset.run <- as.numeric(args$subset)
}
```

@@

```{r subset runs}
if (exists("subset.run")) {
    message(paste0("Subset ", subset.run))
    rds <- rds[[subset.run]]
}

message(rds)
quit()
```
